Computer Science House Constitution

### 2016-04-29 articles.tex
2.B.2 - Semantic Changes
Proposed amendment to modify the amendment process to match the current
method used at house meeting. Targets to resolve wording conflict where
the date of discussion may be ambiguously interpreted.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

@@

% ARTICLE III - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House.
Each carries different qualifications, expectations, and privileges.
When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply.
	\item[Selection:] The process by which an applicant gains membership.
	\item[Expectations:] The duties and responsibilities of House members.
	\item[Privileges:] The benefits offered to House members.
	\item[Evaluations:] The process by which a member is reviewed and assessed.
	\item[Leave of Absence:] The process by which a member may leave House for a period of time.
	\item[Resignations:] The process by which a member terminates House membership.
	\item[Term:] The length of time the membership lasts.
\end{description}

\asection{Introductory Membership}
\asubsection{Introductory Membership Qualifications}
Introductory Membership is open to all students at the Rochester Institute of Technology.
\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evaluations Director.
They must then undergo the selection process as defined in \ref{Selection Processes}.
\asubsection{Introductory Membership Expectations}
Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
\asubsection{Introductory Membership Privileges}
Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
\asubsection{Introductory Membership Evaluations}
Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
\asubsection{Introductory Membership Leave of Absence}
After completion of the Introductory Packet, an Introductory Member may request a leave of absence through the process described in \ref{Leave of Absence}. Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
\asubsection{Introductory Membership Resignations}
Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
\asubsection{Introductory Membership Term}
Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Leave of Absence}
An Active Member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member. Computer Science House recognizes the need for its members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return. Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave begins immediately. A member is allowed to be physically present and also be on a leave of absence. The leave of absence can also be applied retroactively to the member at the discretion of the Evaluations Director.
\asubsection{Leave of Absence Request}
A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave. The request is then given to a staff member of Residence Life, excluding student employees, for approval. At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
\asubsection{Leave of Absence Duration}
A leave of absence can be granted for up to the length of one semester.
\asubsection{Leave of Absence Extension}
A leave of absence can be extended by submitting a new request.
\asubsection{Leave of Absence Return}
A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writing notify the Evaluations Director to end their leave.
\asubsection{Leave of Absence for an Executive Board Member}
The duties and responsibilities of an Executive Board Member on leave are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the member returns from their leave.

>>>>

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.
Any modifications to the written proposal must be posted in the House during the week following the proposal.
The final proposal is presented one week following the proposal's initial introduction at House Meeting for discussion.
Ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

@@

% ARTICLE III - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House.
Each carries different qualifications, expectations, and privileges.
When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply.
	\item[Selection:] The process by which an applicant gains membership.
	\item[Expectations:] The duties and responsibilities of House members.
	\item[Privileges:] The benefits offered to House members.
	\item[Evaluations:] The process by which a member is reviewed and assessed.
	\item[Resignations:] The process by which a member terminates House membership.
	\item[Term:] The length of time the membership lasts.
\end{description}

\asection{Introductory Membership}
\asubsection{Introductory Membership Qualifications}
Introductory Membership is open to all students at the Rochester Institute of Technology.
\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evaluations Director.
They must then undergo the selection process as defined in \ref{Selection Processes}.
\asubsection{Introductory Membership Expectations}
Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
\asubsection{Introductory Membership Privileges}
Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
\asubsection{Introductory Membership Evaluations}
Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
\asubsection{Introductory Membership Resignations}
Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
\asubsection{Introductory Membership Term}
Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

@@
